---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# JABmisc

<!-- badges: start -->
<!-- badges: end -->

The goal of JABmisc is to improve data analysis workflows by: 

1. simplifying initial data exploration
2. providing functions to fill gaps in data manipulation/munging/wrangling


## Installation

JABmisc currently only exists in a development version. You can install this version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("allenbaron/JABmisc")
```


## Examples

To get a quick look at a tabular dataset (after loading) use `describe_cols()` or the full-functioning `audit_df()`. Here's an example with the `airquality` dataset:

```{r example}
library(JABmisc)
describe_cols(airquality)
```

Other available functions in this package:

- filter lists by name or value (`filter_list()`)
- perform numeric formatting (`round_up()`, `format_num()`)
- or, are _TOTALLY_ miscellaneous and provide functionality to help in random, odd use-cases where I've needed them (e.g. `find_consensus_path()`)
